
---
output: github_document
---

# Programming Assignment 1

## Values
```{r}
dur_hablo_stressed <- 0.415
dur_hablo_unstressed <- 0.333
dur_o_stressed <- 0.132
dur_o_unstressed <- 0.077
int_o_stressed <- 84.92
int_o_unstressed <- 84.44
f0_o_stressed <- 171.23
f0_o_unstressed <- 195.86
```

## Operations
```{r}
# Difference in ms between “hablo” and “habló”
dur_diff_word <- dur_hablo_unstressed - dur_hablo_stressed

dur_diff_word

# Difference in ms between the stressed and unstressed [o]
dur_diff_vowel <- dur_o_unstressed - dur_o_stressed

dur_diff_vowel

# Difference in intensity between the stressed and unstressed [o]
int_diff_vowel <- int_o_stressed - int_o_unstressed

int_diff_vowel

# Difference in F0 between the stressed and unstressed [o]
f0_diff_vowel <- f0_o_stressed - f0_o_unstressed

f0_diff_vowel
```

## Observations
The words *hablo* and *habló* have different duration. *Hablo* is 0.082ms shorter than *habló*. As for the difference in duration in both unstressed and stressed [o], the latter is 0.055ms longer than its unstressed counterpart. 

There are also differences in the intensity and F0 at the midpoint of the unstressed and stressed [o]. The difference in intensity between these vowels is 0.48 dB, having the stressed [o] a higher intensity. As for the F0, there is a difference of -24.64 Hz between the stressed and the unstressed [o], having the former a lower pitch. 
